---
pagetitle: "About" 
---

## Authors 

```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=TRUE}
knitr::opts_chunk$set(echo = F, message=F, warning=F)

library(here)
library(tidyverse)
library(htmltools)
library(hrbrthemes)
library(sjmisc)
library(pander)

breve_descricao <- ""

membros <- list(
    luiz <- list(
        nome ="Luíz Fernando Esser",
        email = "luizesser@gmail.com",
        foto = "./assets/authors/luiz.jpg",
        tamanho_foto = "80%",
        afiliacao = "Universidade Federal do Rio Grande do Sul",
        afiliacao_link = "http://www.ufrgs.br/",
        afiliacao_abrev = "Departamento de Botânica",
        papel = "UFRGS"
    ),
    reginaldo <- list(
        nome ="Reginaldo Ré",
        email = "reginaldo@utfpr.edu.br",
        foto = "./assets/authors/reginaldo.jpg",
        tamanho_foto = "69%",
        afiliacao = "Universidade Tecnológica Federal do Paraná",
        afiliacao_link = "http://dacom.cm.utfpr.edu.br/portal",
        afiliacao_abrev = "Departamento de Computação",
        papel = "UTFPR Campo Mourão"
    ),
    vincent <- list(
        nome ="Vincent Montade",
        email = "vincent.montade@gmail.com",
        foto = "./assets/authors/vincent.webp",
        tamanho_foto = "76%",
        afiliacao = "Université de Montpellier, Montpellier, France",
        afiliacao_link = "https://www.umontpellier.fr",
        afiliacao_abrev = "UM",
        papel = "Université de Montpellier"  
    ),
    danilo <- list(
        nome ="Danilo Neves",
        email = "vincent.montade@gmail.com",
        foto = "./assets/authors/danilo.png",
        tamanho_foto = "81%",
        afiliacao = "Universidade Federal de Minas Gerais, Belo Horizonte, Brazil",
        afiliacao_link = "https://ufmg.br/",
        afiliacao_abrev = "UFMG",
        papel = "Universidade Federal de Minas Gerais"  
    )
)
```


```{r echo=FALSE}
tag_container <- tags$div(class="container")

tag_heading <- tags$div(
    class = "heading-title text-center",
    tags$h3(class = "text-uppercase", ""),
    tags$p(class = "p-top-30 half-txt", breve_descricao)
) 

lista_rows <- list() 
for (i in 1:ceiling(length(membros)/4)){
    lista_html_membros <- list()
    
    for (j in 1:4) {
        if (j+((i-1)*4) > length(membros)){
            break();
        }
        membro <- membros[[j+((i-1)*4)]]
        lista_html_membros <- lista_html_membros %>% 
            c(list(
                tags$div(class = "col-md-3 col-sm-3",
                    tags$div(class = "team-member",
                         tags$div(class = "team-img",
                            tags$img(
                                 src = membro$foto,
                                 alt = "team member",
                                 class = "img-responsive",
                                 style = paste0(
                                     "margin:auto;top: 0; left:0; right:0; bottom:0;display: block; width:",
                                     membro$tamanho_foto
                                 )
                            )
                         ),
                        tags$div(class = "team-hover",
                            tags$div(class = "desk",
                                tags$h4(membro$afiliacao),
                                tags$p(membro$papel)),
                            tags$div(class = "s-link",
                                tags$a(membro$afiliacao_abrev, href = membro$afiliacao_link)
                            )
                        ),
                    ),    
                    tags$div(class = "team-title",
                             tags$h5(membro$nome),
                             tags$p(membro$email)
                    )
                )
            ))
    }
    lista_rows <- lista_rows %>%
        c(list(tags$div(class="row",
                lista_html_membros
             )
        ))
}


html_doc <- tagAppendChild(
                tag_container, 
                tagAppendChild(tag_heading, 
                    tagAppendChild(tags$br(), list(tags$br(), tags$br(), lista_rows))
                )
            )

html_doc
```


## Authors Contributions  

DN and VM conceived the idea and reviewed the final manuscript; LFE and RR designed methodology. LFE analyzed the data and led the writing. All authors gave final approval for publication.

## Acknowledgements

This study was financed in part by the Coordenação de Aperfeiçoamento de Pessoal de Nível Superior - Brasil (CAPES) - Finance Code 001. LFE was supported by CAPES PhD scholarship.



## Data Availability
NTT dataset is fully available at http://neotroptree.info. R script is available in Supplementary. Model generated for the Atlantic Rainforest is available by request.



